\thetitle

### 2013-04-13 tfpie/tfpie.tex
acks

>>>>

\subsection*{Acknowledgements}

Matthias Felleisen's approach to pedagody and passion for
undergraduate teaching has inspired this work from the beginning.
CCIS Dean Larry Finkelstein allowed two postdocs to redesign a key
undergraduate course.  Our teaching assistants, Dan Brown, Asumu
Takikawa, and Nicholas Labich, as well as the tutors and graders,
contributed enormously to the success of our courses. Finally, and
most importantly, our students at Northeastern for the last three
years have put up with a curriculum in progress, and the opportunity
to teach them has been truly rewarding.
